Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-07-07 draftfinalreport_v4.Rnw
Generate the proportion immune table from PopnImmunityAll.csv and update caption for input from Tom.

# proportions of the naive population the would be covered if vaccinated by age groups now
propvCohort<-c(
round((sum(naive$Naive[3:6])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:12])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:26])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:36])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:47])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:26])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:36])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:47])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:30])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:45])/sum(naive$Naive)),2),
round((sum(naive$Naive[8:100])/sum(naive$Naive)),2))
yr_range<-c("2-5","5-11","5-16","5-18","5-25","5-35","5-46","11-16","11-18","19-25","19-35","19-46","0-29","0-44",">8")
propvCohort<-cbind(yr_range,propvCohort)
propvCohort<-as.data.frame(propvCohort)
write.table(propvCohort,"vaccine_proportions_Cohort.txt",sep=",",row.names=T,col.names=F)
propsv = NULL
for (i in 1:20 ) {
  propsv[i] = round((sum(naive$Naive[i:13])/sum(naive$Naive)),2)
}
propsvAge = NULL
for (i in 1:20 ) {
  propsvAge[i]=paste(c(min(i:20)-1, max(i:20)-1),collapse="-")
}

>>>>

# proportions of the naive population the would be covered if vaccinated by age groups now
propvCohort<-c(
round((sum(naive$Naive[3:6])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:12])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[6:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:17])/sum(naive$Naive)),2),
round((sum(naive$Naive[12:19])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:26])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:36])/sum(naive$Naive)),2),
round((sum(naive$Naive[20:47])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:30])/sum(naive$Naive)),2),
round((sum(naive$Naive[1:45])/sum(naive$Naive)),2),
round((sum(naive$Naive[8:100])/sum(naive$Naive)),2))
yr_range<-c("2-5","5-11","5-16","5-18","11-16","11-18","19-25","19-30","19-46","0-29","0-44",">8")
propvCohort<-cbind(yr_range,propvCohort)
propvCohort<-as.data.frame(propvCohort)
write.table(propvCohort,"vaccine_proportions_Cohort.txt",sep=",",row.names=T,col.names=F)
propsv = NULL
for (i in 1:20 ) {
  propsv[i] = round((sum(naive$Naive[i:13])/sum(naive$Naive)),2)
}
propsvAge = NULL
for (i in 1:20 ) {
  propsvAge[i]=paste(c(min(i:20)-1, max(i:20)-1),collapse="-")
}
